```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# Identifiers {#identifiers}

Taxonomic identifiers are a central concept in `taxize` - and around which many things depend on. We often either need to get to an identifier for each name the user has, or take an identifier to do something else, for example to get a taxonomic classification.

## Usage {#search-usage}

```{r}
library(taxize)
```

## get functions

There's a family of functions, each targeted at a specific data source, for getting taxonomic identifiers from names. They all start with the prefix `get_`, and end with an abbreviation for the data source. They are:

```{r echo=FALSE, comment=NA, results='asis'}
cat(paste(" -", paste(sprintf("`%s`", grep("get_genes|get_seqs", grep("get_[A-Za-z]+$", getNamespaceExports("taxize"), value = TRUE), value = TRUE, invert=TRUE)), collapse = "\n - ")))
```

Another set of related functions with a trailing underscore (e.g., `get_uid_()`) are available for all data sources, but they do not do interactive usage, but instead provide all data.

## get functions return objects

The returned data from `get_*` functions is either an `NA` if no match, or a character string or numeric if a match. The length can be greater than one as all the functions are vectorized.

There are a number of attributes attached to the output, where each attributes length equals the length of the id vector:

* class: the class of the object
* match: whether a match was found or not
* multiple_matches: whether there were multiple matches or not
* pattern_match: whether there was a match by pattern (i.e., regex)
* uri: the URI/URL for the taxon

An example return from a `get_*` function:

```r
[1] "50157568"
attr(,"class")
[1] "tpsid"
attr(,"match")
[1] "found"
attr(,"multiple_matches")
[1] TRUE
attr(,"pattern_match")
[1] FALSE
attr(,"uri")
[1] "http://tropicos.org/Name/50157568"
```

## identifier notes

* Taxonomic identifiers are unique to the data source. That is, the taxonomic ID for any individual taxon in data source A is different from that in data source B, and different from that in data source C, etc. For example, the taxonomic ID for _Pinus contorta_ in NCBI is `3339`, the ID in ITIS is `183327`, and the ID in COL is `13c40c3f2be0b0965bddf948d2b3115f`.
* Taxonomic identifiers vary among data sources in their structure. That is, some are numeric (only numbers), some are alphanumeric (combination of numbers and letters), and one has an odd structure with letters, numbers and symbols (Nature Serve, e.g., `ELEMENT_GLOBAL.2.147775`). Most data sources provide numeric identifiers. Wikipedia is unusual in that there are no numeric/alphanumeric/etc. taxonomic identifiers for each name - instead they use an "identifier" that is the name.
* ...

## Looking up taxa on the web

If you want to look up the taxon page for any taxa that you've passed through `get_*` functions you can do so by using the `uri` returned from the function. 

For example:

```{r eval = FALSE}
x <- get_tsn('Pinus contorta')
browseURL(attr(x, 'uri'))
```
