```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# Classification {#classification}

The `classification()` function is one of the workhorses of the `taxize` package. 

A taxonomic classification - or hierarchy - is a fundamental set of information about any taxon. Biological taxonomy is arranged in a hierarchical fashion, with each species taxon name fitting into genera, and genera fitting into families, and so on all the way up to just a few categories of very high level organization. 

## Usage {#classification-usage}

```{r}
library(taxize)
```


`classification()` has a number of high level features:

* It is vectorized. That is, it accepts any number of inputs and the output length should equal the input length
* It accepts various inputs:
    * Taxonomic names as character strings
    * Taxonomic identifiers as character stings or numeric values
    * Any output of the various `get_*()` functions
* When there is data available, it always returns a data.frame, facilitating use downstream


## Other sections?

asdfadfasdf

## Related {#classification-related}

Related functions include (note to self: link to these sections when available): 

* `children`
* `downstream`
* `upstream`
* `lowest_common`
