```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# Progress and state {#progress-state}

In `taxize` `v0.9.8` a new set of features was introduced to keep
track of progress of going through each name passed to `get_*()` functions,
better messages about progress and better summary info, and the ability
to restart from where you left off if a `get_*()` function gets interrupted.

## Progress {#progress}

Within each `get_*()` function we keep track of progress. We do this
using the `progressor` R6 class, an internal `taxize` class. `progessor`
is not meant to be used by the taxize user. Within each `get_*()` function
we initiate a new progress object:

```r
prog <- progressor$new(...)
```

As the `get_*()` function progresses the `prog` object is updated with
data and metadata as each name is gone through in the for loop. In addition,
`prog` handles nice print statements and summary info, which can
also be suppressed as needed.

`progressor` is not exported but when you have `taxize` loaded you
can go to its manual file (`?progressor`) to dig into how it works.

`taxize_options()` is a new function in `taxize`, introduced in `v.0.9.8`.
It is meant to manage package wide options in general. The first option it
has is `taxon_state_messages`, which is a boolean (default: `TRUE`) which
controls messages printed by `progressor` - you can set
`taxon_state_messages=FALSE` if you want to suppress messages from
`progressor`.

Messages look like:

```r
get_uid(c("Chironomus riparius", "howdy"))
#> ══  2 queries  ═══════════════
#> 
#> Retrieving data for taxon 'Chironomus riparius'
#> 
#> ✔  Found:  Chironomus+riparius
#> 
#> Retrieving data for taxon 'howdy'
#> 
#> ✖  Not Found:  foo bar
#> ══  Results  ═════════════════
#> 
#> ● Total: 2
#> ● Found: 1
#> ● Not Found: 1
```

Giving:

- `2 queries`: number of names being searched
- `Retrieving data for ...`: which name is being searched
- `✔  Found: ...`: when a name is found, there's a `✔` and the name
- `✖  Not Found: ...`: when a name is not found, there's a `✖` and the name
- At the end is a summary of number of names searched, number of names
found and number of names not found

## State {#state}

The first parameter of every `get_*()` function now accepts either one or
more taxonomic names _OR_ a `taxon_state` object. A `taxon_state` object is
an R6 object that helps keep track of where you are in a `get_*()` function
call. The TLDR is that it means if you're `get_*()` function gets interrupted
because of any number of things (e.g., internet goes out, the dreaded curl
timeout, you hit the wrong key, the remote data provider temporarily goes down)
you can call `taxon_last()` and pass that in to your `get_*()` function to
start from where you left off before the interruption.

```{r}
spp <- names_list("species", 3)
res <- get_gbifid(spp)
z <- taxon_last()
z
z$taxa_remaining()
z$taxa_completed()
z$count # active binding; no parens needed
```

See `?taxon_state` with `taxize` loaded to get all the details on working
with taxon state objects.
