--- 
title: "taxize book"
date: "`r paste0('built on ', Sys.Date(), ' - for taxize v', packageVersion('taxize'))`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: ropensci-books/taxize
description: "taxize manual"
---

# taxize manual

An R package for taxonomic information from around the web. 

`taxize` interacts with a suite of web APIs for taxonomic tasks,
such as getting database specific taxonomic identifiers, verifying
species names, getting taxonomic hierarchies, fetching downstream and
upstream taxonomic names, getting taxonomic synonyms, converting
scientific to common names and vice versa, and more.

## Info

* Code: <https://github.com/ropensci/taxize/>
* Issues/Bug reports: <https://github.com/ropensci/taxize/issues>
* CRAN: <https://cran.rstudio.com/web/packages/taxize/>

## Citing taxize

> Scott Chamberlain and Eduard Szocs (2013). taxize - taxonomic search
> and retrieval in R. F1000Research, 2:191. URL:
> http://f1000research.com/articles/2-191/v2.

> Scott Chamberlain, Eduard Szoecs, Zachary Foster, Zebulun Arendsee,
> Carl Boettiger, Karthik Ram, Ignasi Bartomeus, John Baumgartner,
> James O'Donnell, Jari Oksanen, Bastian Greshake Tzovaras,
> Philippe Marchand, Vinh Tran, Maëlle Salmon, Gaopeng Li,
> and Matthias Grenié. (2019) taxize: Taxonomic information from
> around the web. R package v0.9.9. https://github.com/ropensci/taxize

## Installation

Stable version from CRAN

```{r eval=FALSE}
install.packages("taxize")
```

Development version from GitHub

```{r eval=FALSE}
remotes::install_github("ropensci/taxize")
```

Load library

```{r}
library('taxize')
```
